---
title: "Institutions"
format: html
params:
  refresh_investigator_data: true
  refresh_volumes_sharing_data: true
  save_volumes_sharing_status_info: true
  csv_path: "private"
  truncate_n_chars: 35
---

## About

This page provides information about Databrary's institutional partners.

For more information about institutional roles and responsibilities, see the [Databrary Guide](https://databrary.github.io/guide).

```{r}
#| label: set-up
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

suppressPackageStartupMessages(library(databraryr))
suppressPackageStartupMessages(library(tidyverse))

# Source functions
fl <- list.files(file.path(here::here(), "R"), "*.R", 
                 full.names = TRUE)
p <- purrr::map(fl, suppressPackageStartupMessages(source)) |>
  purrr::quietly()

# Login to Databrary
x <- login_db(email = Sys.getenv("USERNAME"),
         password = Sys.getenv("PASSWORD"),
         client_id = Sys.getenv("CLIENT_ID"),
         client_secret = Sys.getenv("CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

## Summary

```{r}
#| label: gather-institutional-data

if (is.null(params$truncate_n_chars)) {
  params$truncate_n_chars <- 30
}

institutions <- list_institutions() |>
  dplyr::mutate(institution_name = stringr::str_sub(institution_name,                                                  start = 1, end = params$truncate_n_chars),
                institution_url = paste0("<a href='", institution_url, "'>", institution_url, "</a>")) |>
  dplyr::rename(id = institution_id,
                institution = institution_name,
                url = institution_url)
```

Databrary has n=`{r} dim(institutions)[1]` active institutional partners.

## Recent additions

```{r}
#| label: tbl-institutions-recent-additions
#| tbl-cap: "List of the 10 most recent additions to the network of Databrary institutions."
institutions |> 
  dplyr::arrange(desc(id)) |> 
  dplyr::select(institution, url) |>
  head(n = 10) |>
  kableExtra::kbl(format = "html", escape = FALSE) |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"),
                            full_width = FALSE) |>
  kableExtra::scroll_box(width = "800px")
```

## Full list

::: {.callout-warning}
This is a work-in-progress.
:::

Here is a full list in alphabetical order.

```{r}
#| label: tbl-databrary-institutions
#| tbl-cap: "List of all Databrary institutions in alphabetical order."
institutions |>
  dplyr::select(institution, url) |>
  kableExtra::kbl(format = "html", escape = FALSE) |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px", height = "500px")
```

## Map

::: {.callout-warning}
This is a work-in-progress.
:::

## Institutional footprint

This section summarizes which institutions have the largest number of volumes and Authorized Investigators.

::: {.panel-tabset}

## By number of volumes

```{r}
#| label: gather-institutional-volume-data
#| eval: true
#| message: false
#| warning: false

# Load saved csvs
fl <- list.files(file.path(params$csv_path, "user_vol_sharing"), "*.csv", full.names = TRUE)

vol_info <- purrr::map(fl, readr::read_csv, show_col_types = FALSE) |>
  purrr::list_rbind() |>
  dplyr::filter(n_vols > 0)

# Combine user-level and institution-level data
vol_info <- dplyr::left_join(vol_info, institutions, by = join_by(user_affiliation_id == id, user_affiliation == institution))

inst_vols <- vol_info |>
  dplyr::group_by(user_affiliation, user_affiliation_id) |>
  # Eliminate n_private until we can gather that data accurately.
  # summarise(n_ais = n(),
  #           tot_vols = sum(n_vols),
  #           tot_public = sum(n_public),
  #           tot_overview = sum(n_overview),
  #           tot_private = sum(n_private))
  dplyr::summarise(
    n_ais = n(),
    tot_vols = sum(n_vols),
    tot_public = sum(n_public),
    tot_overview = sum(n_overview)
  ) |>
  dplyr::mutate(user_affiliation = stringr::str_sub(user_affiliation, start = 1, end = 30)) |>
  dplyr::mutate(
    user_affiliation = paste0(
      "<a href='https://databrary.org/institution/",
      user_affiliation_id,
      "'>",
      user_affiliation,
      "</a>"
    )
  )
```

```{r}
#| label: tbl-institutional-footprint-vols
#| tbl-cap: "Institutions with the largest number of shared or partially shared volumes. Note that the institution names have been truncated at 25 characters."
#| eval: true
#| message: false
#| warning: false
inst_vols |>
  arrange(desc(tot_vols)) |>
  rename(institution = user_affiliation) |>
  select(c("institution", "tot_vols", "tot_public", "tot_overview")) |>
  kableExtra::kbl(format = "html", escape = FALSE) |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px")
```

## By number of investigators

```{r}
#| label: tbl-institutional-footprint-ais
#| tbl-cap: "Institutions with the largest number of AIs."
#| eval: true
#| message: false
#| warning: false
inst_vols |>
  arrange(desc(n_ais)) |>
  rename(institution = user_affiliation) |>
  kableExtra::kbl(format = "html", escape = FALSE) |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px")
```

:::

## Clean up

Logout from Databrary.

```{r}
#| label: clean-up-logout
x <- logout_db()
```