---
title: "Investigators"
format: html
params:
  refresh_investigator_data: false
  refresh_volumes_sharing_data: false
  save_volumes_sharing_status_info: false
  csv_path: "private"
---

## About

This page provides information about Databrary's authorized investigators.

For more information about Databrary's restricted access policies and the roles and responsibilities of authorized investigators, see the [Databrary Guide](https://databrary.github.io/guide).

```{r}
#| label: set-up
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

suppressPackageStartupMessages(library(databraryr))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(fs))

# Source functions
fl <- list.files(file.path(here::here(), "R"), "*.R", 
                 full.names = TRUE)
p <- purrr::map(fl, suppressPackageStartupMessages(source)) |>
  purrr::quietly()

# Login to Databrary
x <- login_db(email = Sys.getenv("USERNAME"),
         password = Sys.getenv("PASSWORD"),
         client_id = Sys.getenv("CLIENT_ID"),
         client_secret = Sys.getenv("CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

## Summary

```{r}
#| label: gather-investigator-data
#| message: false
#| warning: false
#| 
save_path <- file.path(params$csv_path)
x <- assertthat::is.string(save_path)
x <- assertthat::is.writeable(save_path)

now_str <- lubridate::as_datetime(lubridate::now()) |>
  stringr::str_replace_all(pattern = "[: \\.]", "-")

fn <- file.path(save_path, paste0("investigators-", now_str, ".csv"))

if (params$refresh_investigator_data) {
  investigators <- list_users(include_suspended = FALSE,
                              is_authorized_investigator = TRUE,
                              exclude_self = FALSE)
  readr::write_csv(investigators, fn)
} else {
  fns <- list.files(save_path, pattern = "investigators-", full.names = TRUE)
  # Newest last
  fn <- fns[length(fns)]
  x <- assertthat::is.readable(fn)
  
  investigators <- readr::read_csv(fn, show_col_types = FALSE)
}
```

Databrary has n=`{r} dim(investigators)[1]` active authorized investigators.

## Recent additions

```{r}
#| label: tbl-recent-investigator-additions
#| tbl-cap: "Recently authorized investigators and their institutions."
investigators |> 
  dplyr::arrange(desc(user_id)) |> 
  dplyr::select(user_last_name, user_first_name, user_affiliation_name) |>
  head(n = 10) |>
  kableExtra::kbl() |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px")
```

## Full list

::: {.callout-warning}
This is a work-in-progress.
:::

Here is a full list in alphabetical order.

```{r}
#| label: tbl-databrary-authorized-investigators
#| tbl-cap: "Full list of authorized investigators sorted by last name."
investigators |>
  dplyr::select(user_last_name, user_first_name, user_affiliation_name) |>
  dplyr::arrange(user_last_name) |>
  kableExtra::kbl() |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px", height = "500px")
```

## Numbers of volumes

```{r}
#| label: save-volume-sharing-status-info
#| message: false
#| warning: false
#| echo: false

ai_ids <- investigators$user_id |>
  sort()

f_save_path <- file.path(params$csv_path, "user_vol_sharing")
x <- assertthat::is.string(f_save_path)
y <- assertthat::is.writeable(f_save_path)

msg <- "Load previously saved data about volume sharing status."

if (params$refresh_volumes_sharing_data) {
  msg <- "Gathering fresh volume sharing data."
  
  # Save current to _OLD*
  old_f_save_path <- file.path(params$csv_path, "_OLD_user_vol_sharing")
  x <- assertthat::is.string(old_f_save_path)
  x <- assertthat::is.writeable(old_f_save_path)
  file.copy(from = f_save_path, 
            to = old_f_save_path)
  fs::dir_delete(f_save_path)
  fs::dir_create(f_save_path)
  
  # Save CSVs of volumes owned by authorized investigators
  purrr::map(
    ai_ids,
    save_volumes_sharing_status_info,
    save_path = file.path(params$csv_path, "user_vol_sharing"))
    
  } else {
  msg <- "Volumes shared by owners use archived data."
}
```

`{r} msg`

```{r}
#| label: tbl-volumes-sharing-status
#| tbl-cap: "Users with shared volumes by number of total volumes."
#| eval: true
#| message: false
#| warning: false

# Load saved csvs
fl <- list.files(file.path(here::here(), "private", "user_vol_sharing"),
                 "*.csv",
                 full.names = TRUE)
vol_info <- purrr::map(fl, readr::read_csv, show_col_types = FALSE) |>
  purrr::list_rbind()

# Make table
vol_info |>
  dplyr::select(
    user_first_name,
    user_last_name,
    user_id,
    # user_affiliation,
    n_vols,
    n_public,
    n_overview,
    n_private
  ) |>
  dplyr::rename(first = user_first_name,
                last = user_last_name,
                id = user_id) |>
  dplyr::filter(n_vols > 0) |>
  dplyr::arrange(desc(n_vols)) |>
  kableExtra::kbl() |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra::scroll_box(width = "800px", height = "500px")
```

<!-- ## Number of Sponsored Researchers^[This is a new term for *Affiliates*.] -->

## Clean up

Logout from Databrary.

```{r}
#| label: clean-up-logout
l <- logout_db()
```