---
title: "Investigators"
format: html
params:
  refresh_investigator_data: true
  refresh_volumes_sharing_data: true
  save_volumes_sharing_status_info: false
  csv_path: "private"
---

## About

This page provides information about Databrary's authorized investigators.

For more information about Databrary's restricted access policies and the roles and responsibilities of authorized investigators, see the [Databrary Guide](https://databrary.github.io/guide).

```{r}
#| label: set-up
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

suppressPackageStartupMessages(library(databraryr))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(fs))

# Source functions
fl <- list.files(file.path(here::here(), "R"), "*.R", 
                 full.names = TRUE)
p <- purrr::map(fl, suppressPackageStartupMessages(source)) |>
  purrr::quietly()

# Login to Databrary
x <-login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE,
         vb = TRUE)
```

## Summary

```{r}
#| label: import-inst-affils-data

inst_affil_path <- file.path(params$csv_path, "inst_affils")
inst_affil_fl <- list.files(inst_affil_path, pattern = ".csv$", full.names = TRUE)
inst_affils <- purrr::map(inst_affil_fl, readr::read_csv, show_col_types = FALSE) |>
  purrr::list_rbind()
```

```{r}
#| label: import-inst-shared-vols-data

inst_invest_shared_path <- file.path(params$csv_path, "inst_invest_shared")
inst_invest_shared_fl <- list.files(inst_invest_shared_path, pattern = ".csv$", full.names = TRUE)
inst_invest_shared <- purrr::map(inst_invest_shared_fl, readr::read_csv, show_col_types = FALSE) |>
  purrr::list_rbind()
```

```{r}
#| label: export-file-curation
fn <- format(Sys.time(), "%Y-%m-%d")

inst_invest_shared |>
  dplyr::select(first_name, last_name, user_id, n_vols, n_public, n_overview, n_private,inst_id) |>
  dplyr::arrange(desc(n_vols)) |>
  readr::write_csv(file = paste0("private/curation_contacts/", fn, ".csv"))
```

Databrary has n=`{r} length(unique(inst_affils$user_id))` authorized investigators.

## Recent additions

```{r}
#| label: tbl-recent-investigator-additions
#| tbl-cap: "Recently authorized investigators and their institutions."
inst_affils |> 
  dplyr::arrange(desc(user_id)) |>
  dplyr::rename(last_name = user_sortname, first_name = user_prename) |>
  dplyr::select(last_name, first_name, institution_id) |>
  head(n = 10) |>
  kableExtra::kbl() |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "700px")
```

## Full list

Here is a full list in alphabetical order.

```{r}
#| label: tbl-databrary-authorized-investigators
#| tbl-cap: "Full list of authorized investigators sorted by last name."
inst_affils |>
  dplyr::rename(last_name = user_sortname, first_name = user_prename) |>
  dplyr::select(last_name, first_name, institution_id) |>
  dplyr::arrange(last_name) |>
  kableExtra::kbl() |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra::scroll_box(width = "700px", height = "500px")
```

## Numbers of volumes

```{r}
#| label: get-ais-with-shared-vols
#| eval: true
#| message: false
#| warning: false

ais_w_shared_vols <- inst_invest_shared |>
  dplyr::select(
    first_name,
    last_name,
    user_id,
    inst_id,
    n_vols,
    n_public,
    n_overview
  ) |>
  dplyr::filter(n_vols > 0) |>
  dplyr::arrange(desc(n_vols))

n_ais_total <- length(unique(inst_affils$user_id))
n_ais_sharing <- length(unique(ais_w_shared_vols$user_id))
p_ais_sharing <- n_ais_sharing/n_ais_total
```

Of the n=`{r} n_ais_total` total Authorized Investigators, n=`{r} n_ais_sharing` have shared volumes. This is `{r} round(100*p_ais_sharing, 2)`% of the total Authorized Investigators.

```{r}
#| label: tbl-volumes-sharing-status
#| tbl-cap: "Users with shared volumes by number of total volumes."
ais_w_shared_vols |>
  kableExtra::kbl() |>
  kableExtra::kable_material(full_width = F) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra::scroll_box(width = "700px", height = "500px")
```

## Clean up

Logout from Databrary.

```{r}
#| label: clean-up-logout
l <- logout_db()
```