# Institutions & investigators

This page provides information about Databrary's partner institutions and the investigators they have authorized.

## Institutions {-}

```{r inst-inv-setup}
targets::tar_load(inst_df, store = "../_targets/")

inst_daa_df <- inst_df |>
  dplyr::filter(daa == TRUE)
```

There are *n*= `r dim(inst_df)[1]` total institutions in the Databrary system.

Of these, *n*= `r dim(inst_daa_df)[1]` or `r paste0(format(dim(inst_daa_df)[1]/dim(inst_df)[1] * 100, digits = 3, nsmall = 1), "%")` have active Databrary Access Agreements (DAA).
Institutions *without* active DAAs have typically had a single authorized user leave the institution or are institutions that would not typically authorize individual researchers, e.g., government agencies or professional societies. 

### Institutions with inactive DAAs {-}

The following institutions do not have active DAAs:

<!-- Here is how to make "clickable" links in tables created by kable(): https://stackoverflow.com/questions/66528695/r-kableextra-create-column-with-link#:~:text=You%20add%20clickable%20images%20by,statement%20to%20make%20it%20work. -->

```{r inactive-daas}
inst_df |>
  dplyr::filter(daa == FALSE) |>
  dplyr::filter(!(inst_id %in% c(8545, 8717, 8720, 9238, 10551, 12569))) |>
  dplyr::select(c('inst_id', 'inst_name')) |>
  dplyr::mutate(url = paste0("https://databrary.org/party/", inst_id)) |>
  dplyr::mutate(name = paste0("<a href='", url, "'>", inst_name, "</a>")) |>
  dplyr::select(inst_id, name) |>
  kableExtra::kable(format = 'html', escape = FALSE) |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

## Map of institutions {-}

```{r inst-inv-stadia-map}
#| fig-cap: "Map of worldwide Databrary institutions"
#| label: "fig-institution-map"
inst_daa_df_lat_lon <- inst_daa_df |>
  dplyr::filter(!is.na(lat), !is.na(lon))

world_map <- ggmap::get_stadiamap(bbox = c(-179, -65, 179, 65), zoom = 1, maptype = "stamen_terrain_background")

ggmap::ggmap(world_map) +
  ggplot2::geom_point(data = inst_daa_df_lat_lon, color = I("red"), size = 0.3)
```

Here is an alternative map from Google maps that we do not render for now because the Google Maps API throttles queries too often.

```{r inst-inv-map, eval=FALSE}
ggmap::get_googlemap("Spain", zoom = 1) |>
  ggmap::ggmap(maprange = TRUE) + 
  ggplot2::geom_point(data = inst_daa_df, color = I("red")) +
  ggplot2::xlim(c(-180, 180)) +
  ggplot2::ylim(c(-60, 60))
```

## Investigators per institution {-}

```{r inst-inv-ai-stats}
ai_stats <- fivenum(inst_daa_df$n_auth_invest)
```

The number of authorized investigators/institution is in the range of [`r ai_stats[1]`, `r ai_stats[5]`], with a median of `r ai_stats[3]` and a mean of `r format(mean(inst_daa_df$n_auth_invest), digits = 3, nsmall = 1)`.

```{r}
#| fig-cap: "Distribution of investigators/authorized institution"
#| label: "fig-investigators-per-institution"
inst_daa_df |>
  ggplot2::ggplot() +
  ggplot2::aes(n_auth_invest) +
  ggplot2::geom_histogram(binwidth = 5)
```

### Authorized Investigators by Institution {-}

```{r inst-inv-table-by-ins}
inst_daa_df |>
  dplyr::select(-c("lat", "lon", "daa", "inst_url", "databrary_url")) |>
  dplyr::mutate(url = paste0("https://databrary.org/party/", inst_id)) |>
  dplyr::mutate(name = paste0("<a href='", url, "'>", inst_name, "</a>")) |>
  dplyr::select(inst_id, name, n_auth_invest) |>
  dplyr::arrange(desc(n_auth_invest)) |>
  kableExtra::kable(format = 'html', escape = FALSE) |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

<!-- **TODO**: Add the automatic creation of the JSON file needed to update and render the map on the Databrary home page. -->

## Investigators {-}

Load the database of investigators and select non-duplicate entries.

```{r inst-inv-load-ais}
# tar_load(invest_df, store = "../_targets/")
invest_df <- readr::read_csv(paste0(here::here(), '/src/csv/all-ais.csv'),               show_col_types = FALSE)

invest_df <- dplyr::distinct(invest_df)
```

#### All  {-}

```{r inst-inv-plot-affils-7}
ggplot2::ggplot(invest_df) +
  ggplot2::aes(n_affils) +
  ggplot2::geom_histogram(bins = 20)
```

```{r inst-inv-table-affils-8}
invest_df |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  kableExtra::kable(format = 'html') |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

Computer statistics about the number of affiliates per investigator.

```{r inst-inv-add-affils}
gte2_affils <- invest_df |>
  dplyr::filter(n_affils >= 2) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  dplyr::distinct()
gte5_affils <- invest_df |>
  dplyr::filter(n_affils >= 5) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  dplyr::distinct()
gte10_affils <- invest_df |>
  dplyr::filter(n_affils >= 10) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  dplyr::distinct()
no_affils <- invest_df |>
  dplyr::filter(n_affils < 1) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  dplyr::distinct()
```

There are *n* = `r dim(gte10_affils)[1]` Authorized Investigators with 10 or more affiliates; *n* = `r dim(gte5_affils)[1]` with 5 or more; *n* = `r dim(gte2_affils)[1]` with 2 or more affiliates; and *n* = `r dim(no_affils)[1]` with no affilates.

#### 10+ affiliates {-}

```{r inst-inv-table-affils-1}
ggplot2::ggplot(gte10_affils) +
  ggplot2::aes(n_affils) +
  ggplot2::geom_histogram(bins = 10)
```

```{r inst-inv-table-affils-2}
gte10_affils |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  kableExtra::kbl() |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

#### 5+ affiliates  {-}

```{r inst-inv-table-affils-3}
ggplot2::ggplot(gte5_affils) +
  ggplot2::aes(n_affils) +
  ggplot2::geom_histogram(bins = 10)
```

```{r inst-inv-table-affils-4}
gte5_affils |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  kableExtra::kbl() |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

#### 2+ affiliates {-}

```{r inst-inv-table-affils-5}
ggplot2::ggplot(gte2_affils) +
  ggplot2::aes(n_affils) +
  ggplot2::geom_histogram(bins = 15)
```

```{r inst-inv-table-affils-6}
gte2_affils |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, ai_affiliation, n_affils) |>
  kableExtra::kbl() |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

