# Funders

This document describes funders associated with Databrary volumes (projects).

```{r funders-setup}
targets::tar_load(volume_funders_df, store = "../_targets/")
funders_df <- volume_funders_df |>
  dplyr::distinct()
```

## Volumes by funder {-}

### $n$ volumes listing funders {-}

```{r funder-filter}
vols_w_funders <- funders_df |>
  dplyr::filter(!is.na(funder_id), !is.na(funder_name)) |>
  dplyr::group_by(vol_id)
```

There are $n=$ `r length(unique(vols_w_funders$vol_id))` volumes that list funders.

```{r funders-table}
vols_w_funders |>
  dplyr::select(-funder_id) |>
  kableExtra::kable(format = 'html') |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

### Funders by number of volumes {-}

```{r funders-by-vol}
funders_filtered <- funders_df |>
  dplyr::filter(!is.na(funder_id), !is.na(funder_name)) |>
  dplyr::group_by(funder_name) |>
  dplyr::summarize(n_vols = n()) |>
  dplyr::arrange(desc(n_vols))

funders_filtered |>
  kableExtra::kable(format = 'html') |>
  kableExtra::kable_styling()
```

### NSF-specific data {-}

The following is based on functions created for  <https://databrary.github.io/nsf-oac-2032713/nsf-funding.html>

```{r funders-nsf}
db_w_nsf <- readr::read_csv("csv/databrary-vols-w-nsf-funding-all.csv")

# max_ids_df <- readr::read_csv("csv/max-ids.csv", show_col_types = FALSE)
# 
# if (max_ids_df$MAX_VOL_ID > 1) {
#   max_vol_id <- max_ids_df$MAX_VOL_ID
# } else {
#   message("Cannot extract max_vol_id. Using default of 1772")
#   max_vol_id <- 1772
# }
# 
# db_w_nsf <-
#   purrr::map(1:max_vol_id,
#              get_vol_awards,
#              funder_str = "NSF",
#              .progress = "Databrary vols w/ NSF:") |> 
#   purrr::list_rbind() |>
#   add_clean_nsf_award_id()
# 
# readr::write_csv(db_w_nsf, "csv/databrary-vols-w-nsf-funding-all.csv")
```

There are *n=* `r dim(db_w_nsf)[1]` shared Databrary volumes that list NSF as a funder and *n=* `r unique(db_w_nsf$award_id) |> length()` unique awards.
