---
title: "Institutions"
format: html
params:
  refresh_volumes_sharing_data: false
  csv_path: "private"
---

## About

This page provides information about Databrary's institutional partners.

For more information about institutional roles and responsibilities, see the [Databrary Guide](https://databrary.github.io/guide).

```{r}
#| label: set-up
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

suppressPackageStartupMessages(library(databraryr))
suppressPackageStartupMessages(library(tidyverse))

# Source functions
fl <- list.files(file.path(here::here(), "src", "R"), "*.R", 
                 full.names = TRUE)
p <- purrr::map(fl, suppressPackageStartupMessages(source))

# Login to Databrary
x <- login_db(email = Sys.getenv("DB_LOGIN_ACCT"),
         password = Sys.getenv("DB_LOGIN_PW"),
         client_id = Sys.getenv("DB_API_CLIENT_ID"),
         client_secret = Sys.getenv("DB_API_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

## Summary

```{r}
#| label: gather-institutional-data
institutions <- list_institutions()
```

Databrary has n=`{r} dim(institutions)[1]` active institutional partners.

## Recent additions

```{r}
#| label: tbl-institutions-recent-additions
#| tbl-cap: "List of the 10 most recent additions to the network of Databrary institutions."
institutions |> 
  dplyr::arrange(desc(institution_id)) |> 
  dplyr::select(institution_name, institution_url) |>
  head(n = 10) |>
  kableExtra::kable(format = "html") |>
  kableExtra::kable_material() |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px")
```

## Full list

::: {.callout-warning}
This is a work-in-progress.
:::

Here is a full list in alphabetical order.

```{r}
#| label: tbl-databrary-institutions
#| tbl-caption: "List of all Databrary institutions in alphabetical order."
institutions |>
  dplyr::select(institution_name, institution_url) |>
  kableExtra::kable(format = "html") |>
  kableExtra::kable_material() |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px", height = "500px")
```

## Map

::: {.callout-warning}
This is a work-in-progress.
:::

## Institutional footprint

```{r}
#| label: tbl-institutional-footprint
#| eval: true
#| message: false
#| warning: false

# Load saved csvs
fl <- list.files(file.path(params$csv_path, "user_vol_sharing"), "*.csv", full.names = TRUE)

vol_info <- purrr::map(fl, readr::read_csv, show_col_types = FALSE) |>
  purrr::list_rbind() |>
  dplyr::filter(n_vols > 0)

inst_vols <- vol_info |>
  group_by(user_affiliation) |>
  summarise(n_ais = n(),
            tot_vols = sum(n_vols),
            tot_public = sum(n_public),
            tot_overview = sum(n_overview),
            tot_private = sum(n_private))

inst_vols |>
  arrange(desc(tot_vols)) |>
  kableExtra::kable(format = "html") |>
  kableExtra::kable_material() |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px")
```

## Clean up

Logout from Databrary.

```{r}
#| label: clean-up-logout
logout_db()
```