---
title: "Investigators"
format: html
---

## About

This page provides information about Databrary's authorized investigators.

For more information about Databrary's restricted access policies and the roles and responsibilities of authorized investigators, see the [Databrary Guide](https://databrary.github.io/guide).

```{r}
#| label: set-up
#| echo: FALSE
#| message: FALSE
#| warning: FALSE
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library(dplyr)
library(ggplot2)
library(databraryr)

# Login to Databrary
x <- login_db(email = Sys.getenv("DB_LOGIN_ACCT"),
         password = Sys.getenv("DB_LOGIN_PW"),
         client_id = Sys.getenv("DB_API_CLIENT_ID"),
         client_secret = Sys.getenv("DB_API_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

## Summary

```{r}
#| label: gather-investigator-data
investigators <- list_users(include_suspended = FALSE, is_authorized_investigator = TRUE)
```

Databrary has n=`{r} dim(investigators)[1]` active authorized investigators.

## Recent additions

```{r}
#| label: tbl-recent-investigator-additions
#| tbl-cap: "Recently authorized investigators and their institutions."
investigators |> 
  dplyr::arrange(desc(user_id)) |> 
  dplyr::select(user_last_name, user_first_name, user_affiliation_name) |>
  head(n = 10) |>
  kableExtra::kable(format = "html") |>
  kableExtra::kable_material() |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px")
```

## Full list

::: {.callout-warning}
This is a work-in-progress.
:::

Here is a full list in alphabetical order.

```{r}
#| label: tbl-databrary-authorized-investigators
#| tbl-cap: "Full list of authorized investigators sorted by last name."
investigators |>
  dplyr::select(user_last_name, user_first_name, user_affiliation_name) |>
  dplyr::arrange(user_last_name) |>
  kableExtra::kable(format = "html") |>
  kableExtra::kable_material() |>
  kableExtra:: kable_styling(bootstrap_options = c("striped", "hover")) |>
  kableExtra:: scroll_box(width = "800px", height = "500px")
```

```{r}
#| label: clean-up-logout
logout_db()
```