# Volumes & sessions

This page summarizes the number of shared volumes by sharing type and by investigator.

```{r shared-vol-setup}
targets::tar_load(vols_sess_df, store = "../_targets/")
```

## How shared by unique volume {-}

```{r shared-vols-stats}
unique_vols <- vols_sess_df |>
  dplyr::rename(investigator = owner_name,
                party_id = owner_id,
                sharing_level = public_access) |>
  dplyr::mutate(shared_type = ifelse(sharing_level == "full",
                                     "full_volume", "overview_only")) |>
  dplyr::mutate(vol_url = paste0("https://nyu.databrary.org/volume/", vol_id)) |>
  dplyr::group_by(vol_id,
                  vol_name,
                  vol_url,
                  created_date,
                  shared_type,
                  n_sessions) |>
  dplyr::summarise(n_owners = dplyr::n())
```

There are $n=$ `r dim(unique_vols)[1]` total shared volumes on Databrary.

### Full volume {-}

```{r shared-vols-full}
unique_vols_full <- unique_vols |>
  dplyr::filter(shared_type == "full_volume")
```

There are $n=$ `r dim(unique_vols_full)[1]` volumes fully shared on Databrary.

```{r shared-vols-full-table}
unique_vols_full |>
  dplyr::arrange(desc(n_sessions)) |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

### Overview only {-}

```{r shared-vols-overview}
unique_vols_overview <- unique_vols |>
  dplyr::filter(shared_type == "overview_only")
```

There are $n=$ `r dim(unique_vols_overview)[1]` volume overviews shared on Databrary.

```{r shared-vols-overview-table}
unique_vols_overview |>
  dplyr::arrange(desc(n_sessions)) |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

## How shared by investigator {-}

```{r shared-vols-how-shared}
vols_dat <- vols_sess_df |>
  # change variable names, create full_volume vs. overview_only
  dplyr::group_by(owner_name, owner_id) |>
  dplyr::rename(investigator = owner_name,
                party_id = owner_id,
                sharing_level = public_access) |>
  dplyr::mutate(shared_type = ifelse(sharing_level == "full", "full_volume", "overview_only")) |>
  dplyr::select(investigator,
                party_id,
                vol_id,
                created_date,
                shared_type,
                n_sessions) |>
  dplyr::mutate(url = paste0("https://nyu.databrary.org/party/", party_id)) |>
  dplyr::group_by(investigator, url, shared_type) |>
  # summarise by total shared volumes by type with session stats
  dplyr::summarise(
    n_vols = dplyr::n(),
    tot_sess = sum(n_sessions),
    min_n_sess = min(n_sessions),
    max_n_sess = max(n_sessions)
  ) |>
  dplyr::arrange(shared_type, desc(tot_sess))
```

Sorted by `tot_sess`, the total number of sessions from these Authorized Investigators.

### Full volume {-}

```{r shared-vols-by-ai}
vols_dat |>
  dplyr::filter(shared_type == "full_volume") |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

### Overview only {-}

```{r shared-vols-by-ai-overview}
vols_dat |>
  dplyr::filter(shared_type == "overview_only") |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```
