# Tags & keywords

This page summarizes data about searchable tags on all shared Databrary volumes.

The tags data is updated approximately every 13 weeks.

The most recent tags data were collected on `r file.info("csv/databrary-tags.csv")$mtime`.

```{r tags-setup}
targets::tar_load(volume_tags_df, store = '../_targets/')
tags <- volume_tags_df
```

## Tag stats {-}

```{r tags-stats}
vols_without_tags <- tags |>
  dplyr::filter(is.na(tags))

vols_with_tags <- tags |>
  dplyr::filter(!is.na(tags)) |>
  dplyr::group_by(vol_id) |>
  dplyr::summarise(n_tags = dplyr::n())
```

### Histogram of tags/volume {-}

```{r tags-hist}
vols_with_tags |>
  ggplot2::ggplot() +
  ggplot2::aes(n_tags) +
  ggplot2::geom_histogram(bins = 12)
```

### Unique tags {-}

```{r tags-unique}
unique_tags <- tags |>
  dplyr::select(tags, weight) |>
  dplyr::filter(!is.na(tags)) |>
  dplyr::group_by(tags) |>
  dplyr::summarise(n_vols_using = dplyr::n(), weight_sum = sum(weight)) |>
  dplyr::arrange(desc(n_vols_using))
```

There are `r dim(unique_tags)[1]` unique tags.

```{r tags-unique-table}
unique_tags |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

### Word cloud {-}

```{r tags-wordcloud}
wordcloud::wordcloud(words = unique_tags$tags, 
                     freq = unique_tags$n_vols_using)
```

## Tags by volume {-}

```{r tags-by-vol}
tags |> 
  dplyr::filter(!is.na(weight)) |>
  dplyr::arrange(vol_id, weight) |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

## STEM-relevant tags {-}

This section has been omitted pending a future software update.
